Working title: the most amaz-zing SPIM and how we built it.

### 2015-01-20 latex-style-files-spie-manuscript/manuscript1.0.tex
commit before merge with ludo

Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples. After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition to a detailed description of all opto-mechanical components, we further present a practical guide for the alignment of a LSFM, a non-trivial task whichhas too often been summarised in a single sentence. A systematic approach to handle, store and analyse the data is also given. We further explain about the data volume we produce how it can be reduced and handled. We finish with some nice data and an outlook.  The final sentence of the introduction needs to be amazing.

@@

\section{Sample mounting}
%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering. Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices. Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque. In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed. These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
%
%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining. A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form. Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap. Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies. With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.

@@

We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:Panel1},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:Panel1},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D).

@@

	\subsection{Illumination}

@@

The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to electronically control the frequency with which the polarisation is changed. After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

From here on three different light paths can be chosen through flip mirrors. One light path option guides the light through an axicon (apex angle of $160\degree$) and an achromatic doublet (f50) to create a Bessel beam. The other two options create Gaussian beams of different beam diameter. This diameter variation translates to different fields of view later on in the detection path. The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms. The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.

@@

Fluorescence detection in light sheet microscopy is analogous to conventional wide-field microscopy. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a camera chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to 3ms results in approx. 300 lines being simultaneously exposed. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $80\micro m$ in the sample space. With those values the camera acquires images at a frame rate of 44Hz. Synchronisation of the rolling shutter with the scanned illumination beam results in confocal line detection\cite{Baumgart2012}.

@@

	\subsection{Contrast}
	\subsection{Signal-to-noise ratio}
	\subsection{Optical sectioning}

@@

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
		\begin{tabular}{llll}
		Component												&	Manufacturer															& Part\# 								& Specifications 																											\\\hline
		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																	\\
																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																	\\
																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised														\\
																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised														\\
																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised											\\\hline
		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V						\\\hline
		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth			\\\hline
		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																\\\hline		
		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)													\\
																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)															\\\hline
		\multirow{3}{*}[1.2em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																						\\
																		&																						&	M-122									& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s		\\
																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
		\end{tabular}
\end{table}
\end{landscape}

>>>>

Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples. After briefly presenting the optical clearing protocol we employ to render our samples transparent, we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition to a full description of the optical setup, the control hardware and software, we further present a practical guide for the alignment of a LSFM, a non-trivial task that requires careful consideration. A systematic approach to handle, store and analyse the data is explained in detail. We further explain about the data volume we produce how it can be reduced and handled. The imaging capabilities are demonstrated by 3D reconstructions of biological specimens.  The final sentence of the introduction needs to be amazing.

@@

\section{Sample mounting and motion}
%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering. Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices. Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque. In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed. These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
%
%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining. A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form. Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap. Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies. With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.

@@

We designed a cubic, water-tight sample chamber (Figure\ref{fig:Panel1},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:Panel1},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:Panel1},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of the Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:Panel1},D). Illumination and detection axes are horizontal and the sampler rotation occurs around the vertical axis.

@@

@@

\subsection{Laser unit}		
The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to electronically control the frequency with which the polarisation is changed. After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

\subsection{Illumination unit}		
From here on three different light paths can be chosen through flip mirrors. One light path option guides the light through an axicon (apex angle of $160\degree$) and an achromatic doublet (f50) to create a Bessel beam. The other two options create Gaussian beams of different beam diameter. This diameter variation translates to different fields of view later on in the detection path. The three options are recombined before a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms. The beam is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). The galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to 3ms results in approx. 300 lines being simultaneously exposed. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $80\micro m$ in the sample space. With those values the camera acquires images at a frame rate of 44Hz.

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for a data acquisition and generation device (DAQ) from National Instruments which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012}. For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

@@

	\subsection{Contrast}

	\subsection{Signal-to-noise ratio}

	\subsection{Optical sectioning}

@@

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
		\begin{tabular}{llll}
		Component												&	Manufacturer															& Part\# 								& Specifications 																											\\\hline\hline
		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																	\\
																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																	\\
																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised														\\
																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised														\\
																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised											\\\hline
		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V						\\\hline
		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth			\\\hline
		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																\\\hline		
		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)													\\
																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)															\\\hline
		\multirow{3}{*}[1.2em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																						\\
																		&																						&	M-122									& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s		\\
																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
		\end{tabular}
\end{table}
\end{landscape}
